Comments on binomial graph learning

### 2022-04-12 model specification.Rmd
Added constraints.
Updates to visuals and constraints.

>>>>

* Case $\chi$: Here I imagine the constraints are on the Laplacian

\begin{equation}
\begin{aligned}
&\quad \text{tr}(L) = N, \\
&\quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
&\quad L\cdot \textbf{1} = \textbf{0} \\
\end{aligned}
\end{equation}

* Case with adjacency matrix:

\begin{equation}
\begin{aligned}
&\quad A_{i,j} = 0 \text{ if } i = j, \\
&\quad A_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j
\end{aligned}
\end{equation}

* Consider the quadratic form 
$$
  x^TLx = \frac{1}{2}\sum_{(i,j)\in E}w_{i,j}(f(i) - f(j))^2
$$

Because $x$ is a binomial, this expression sums the weights of edeges with incident nodes that have differing signal values. Suppose the graph has a constant signal, then $x^TLx = 0$. Suppose, we are in the worst case when incident nodes for each edge have a different signal; in this case $x^TLx = \frac{1}{2}\sum_{(i,j) \in E}w_{i,j}$. Note, we can bound $x^TLx$ from below by $\min{w_{i,j}}$ in the case were a single edge has incident nodes with differing signals. We can use these bounds to gauge the quality of model.
